Optimising Heterogeneous Ambulance Fleet Allocations in Jakarta

### 2024-07-29 response/response.tex

\section{Responses to the Editor}

\begin{itemize}

\item The editor wrote:
\begin{quote}
``Please cite relevant, recent work published in this journal. This is by no means mandatory, but it will help to position your work in the context of research published in the journal.''
\end{quote}

\item The editor wrote:
\begin{quote}
``The manuscript does not sufficiently discuss the managerial implications of the work. Please develop this further in your revision.''
\end{quote}
We have now included a paragraph on this in the introduction.

@@

\item Reviewer 2 wrote:
\begin{quote}
``P7 L29 – equations in APPENDIX A.''
\end{quote}
Fixed throughout.

\item Reviewer 2 wrote:
\begin{quote}
``P8 Fig 3 – Include y axis scale''
\end{quote}

\item Reviewer 2 wrote:
\begin{quote}
``P8 L27 – change ending to – This might not have a strong impact on the results of this study.''
\end{quote}
Fixed.

\item Reviewer 2 wrote:
\begin{quote}
``P8 L49 – In addition to the package used, can you more explicitly state what optimisation problem was solved here, and by which method?''
\end{quote}
We have added further explanation detailing how we solve the system of non-linear equations, and have added a reference to the underlying optimisation algorithm used.

### 2024-07-29 tex/main.tex
address MINPACK comment, add daniel's revision, fix min/max comment in algorithm

@@

We propose finding the true vehicle utilisations by first solving
Equation~\ref{eqn:utilisations_primary} for the $\lambda_a$; determining the
primary vehicle utilisations with Equation~\ref{eqn:utilisation_ratio_primary};
then using these to solve Equation~\ref{eqn:utilisations_secondary} for the
$\tilde{\lambda}_a$; and determining the secondary vehicle utilisations with
Equation~\ref{eqn:utilisation_ratio_secondary}. These can be solved
numerically. In our implementation this is solved using the MINPACK hybrd and
hybrj algorithms by using Scipy's \texttt{fsolve} function
\citep{2020SciPy-NMeth}. It should be noted that in this section we assume that
all $\lambda_{pk}$ are static and not time-dependant, which is an assumption
that will be used throughout the optimisation methodology, however in the
simulation we can account for time-dependent demand.

@@

\begin{algorithm}
\algnewcommand\algorithmicto{\textbf{to }}
\caption{Evolutionary Algorithm used to find better allocations.}
\label{alg:heuristic}
\begin{algorithmic}[1]
\State Create a population of $N$ random allocations ($Z_a$, $\tilde{Z}_a$)\;
\For{$i \leftarrow 0$ \algorithmicto $H$}
  \State Rank the population \textcolor{red}{by decreasing expected survival} according to Equation~\ref{eqn:meslmhphf}\;
  \State Keep the top $\kappa$ solutions\;
  \State $m \leftarrow \lceil m_0 - \max\left(m_0, i \times c\right)\rceil$\;
  \For{$j \leftarrow 0$ \algorithmicto $N - \kappa$}
    \State Randomly choose and copy a solution from the population\;
    \State Mutate that copy of the solution $m$ times\;
    \State Place mutated copy in a separate population\;
  \EndFor
  \State Combine populations;\
\EndFor
\State Rank the population according to Equation~\ref{eqn:meslmhphf};\
\State Output the top ranking solution.
\end{algorithmic}
\end{algorithm}

>>>>

\textcolor{red}{There are several managerial implications for EMS providers and
government agencies in Jakarta and Indonesia, respectively. The findings
emphasise the importance of adopting a dynamic and data-driven approach to
resource allocation. The inclusion of a heterogeneous fleet, such as Rapid
Response Vehicles (RRVs) alongside traditional ambulances, has been shown to
significantly improve response times and patient survival rates, particularly in
densely populated urban areas. Managers are advised to invest in these diverse
fleets and adopt flexible allocation strategies that account for temporal
variations in demand, such as the daily influx of commuters and the differing
population densities across neighbourhoods. The research underscores the
necessity of enhancing data collection practices to support informed
decision-making, with the development of user-friendly decision support tools to
assist in visualising data and predicting outcomes}

@@

We propose finding the true vehicle utilisations by first solving
Equation~\ref{eqn:utilisations_primary} for the $\lambda_a$; determining the
primary vehicle utilisations with Equation~\ref{eqn:utilisation_ratio_primary};
then using these to solve Equation~\ref{eqn:utilisations_secondary} for the
$\tilde{\lambda}_a$; and determining the secondary vehicle utilisations with
Equation~\ref{eqn:utilisation_ratio_secondary}. These can be solved
numerically. In our implementation this is solved using the MINPACK hybrd and
hybrj algorithms by using Scipy's \texttt{fsolve} function
\citep{2020SciPy-NMeth}. \textcolor{red}{These algorithms are efficient methods for finding zeros of systems of non-linear equations. They are based on the Powell hybrid method \cite{powell70}.} It should be noted that in this section we assume that
all $\lambda_{pk}$ are static and not time-dependant, which is an assumption
that will be used throughout the optimisation methodology, however in the
simulation we can account for time-dependent demand.

@@

\begin{algorithm}
\algnewcommand\algorithmicto{\textbf{to }}
\caption{Evolutionary Algorithm used to find better allocations.}
\label{alg:heuristic}
\begin{algorithmic}[1]
\State Create a population of $N$ random allocations ($Z_a$, $\tilde{Z}_a$)\;
\For{$i \leftarrow 0$ \algorithmicto $H$}
  \State Rank the population \textcolor{red}{by decreasing expected survival} according to Equation~\ref{eqn:meslmhphf}\;
  \State Keep the top $\kappa$ solutions\;
  \State $m \leftarrow \lceil m_0 - \min\left(m_0, i \times c\right)\rceil$\;
  \For{$j \leftarrow 0$ \algorithmicto $N - \kappa$}
    \State Randomly choose and copy a solution from the population\;
    \State Mutate that copy of the solution $m$ times\;
    \State Place mutated copy in a separate population\;
  \EndFor
  \State Combine populations;\
\EndFor
\State Rank the population according to Equation~\ref{eqn:meslmhphf};\
\State Output the top ranking solution.
\end{algorithmic}
\end{algorithm}
